Parallel Computations for Solving Multicriteria Mixed-Integer Optimization Problems

### 2020-12-13 2021/PСT_GergelKozinov/2021_PCT.tex
2021/PСT_GergelKozinov/2021_PCT.tex
Исправление ошибок в статье.

The rest of the paper is organized as follows. In Section \ref{sec:2}, we give the statement of multicriteria optimization problems, present a minimax scheme for scalarization of the vector efficiency criterion and introduce the concept of multistage solution of multicriteria optimization problems. In Section \ref{sec:3}, we present a description of the proposed approach based on the reduction of mixed-integer optimization problems to solving a family of optimization problems with the use of only continuous parameters. This section also describes a dimensionality reduction scheme, which allows multidimensional optimization problems to be reduced to a one-dimensional global search problem. Section \ref{sec:4} presents a parallel algorithm for solving multicriteria mixed-integer optimization problems, which is used in the framework of the proposed approach. Section \ref{sec:5} contains the results of numerical experiments confirming that the proposed approach is quite promising. In conclusion, the results obtained are discussed and possible main directions for continuing the research are outlined.

@@

To construct a combined scalar efficiency index $F(\alpha,y,u)$ from (\ref{eq:6}), one of the most frequently used scalarization methods is to use a minimax criteria convolution \cite{c2,c5}:
\begin{equation}\label{eq:8}
\begin{matrix}
  F(\lambda,y,u)=\max{(\lambda_i f_i (y,u),1\leq i \leq s)},\\
  \lambda=(\lambda_1,\lambda_2, \dots, \lambda_s)\in \Lambda \subset R^s: \sum_{i=1}^{s}\lambda_i=1, \lambda_i \geq 0, 1 \leq i \leq s.
\end{matrix}
\end{equation}

@@

The use of dimensionality reduction makes it possible to combine (concatenate) one-dimensional functions $F(a, y(x),w_i)$, $1 \leq i \leq l$, from (\ref{eq:15}) into a single one-dimensional function $\Phi(\alpha,y(x))$, defined over the segment $[0,l]$ (see Fig.~\ref{fig:1}).

@@

\section*{Acknowledgements} 
\hl{This research was supported by the Russian Science Foundation, project No 16-11-10150 ``Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance''}

>>>>

The rest of the paper is organized as follows. In Section \ref{sec:2}, we give the statement of multicriteria optimization problems, present a minimax scheme for scalarization of the vector efficiency criterion and introduce the concept of multistage solution of multicriteria optimization problems. In Section \ref{sec:3}, we present a description of the proposed approach based on the reduction of mixed-integer optimization problems to solving a family of optimization problems with the use of only continuous parameters. This section also describes a dimensionality reduction scheme, which allows multidimensional optimization problems to be reduced to a one-dimensional global search problem. Section \ref{sec:4} presents a parallel algorithm for solving multicriteria mixed-integer optimization problems, which is used in the framework of the proposed approach. Section \ref{sec:5} contains the results of numerical experiments confirming that the proposed approach is promising. In conclusion, the results obtained are discussed and possible main directions for continuing the research are outlined.

@@

To construct a combined scalar efficiency function $F(\alpha,y,u)$ from (\ref{eq:6}), one of the most frequently used scalarization methods is to use a minimax criteria convolution \cite{c2,c5}:
\begin{equation}\label{eq:8}
\begin{matrix}
  F(\lambda,y,u)=\max{(\lambda_i f_i (y,u),1\leq i \leq s)},\\
  \lambda=(\lambda_1,\lambda_2, \dots, \lambda_s)\in \Lambda \subset R^s: \sum_{i=1}^{s}\lambda_i=1, \lambda_i \geq 0, 1 \leq i \leq s.
\end{matrix}
\end{equation}

@@

The use of dimensionality reduction makes it possible to combine (concatenate) one-dimensional functions $F(\alpha, y(x),w_i)$, $1 \leq i \leq l$, from (\ref{eq:15}) into a single one-dimensional function $\Phi(\alpha,y(x))$, defined over the segment $[0,l]$ (see Fig.~\ref{fig:1}).

@@

\section*{Acknowledgements} 
This work was supported by the project no. 0729-2020-0055 and by the Research and Education Mathematical Center, project no. 075-02-2020-1483/1
